---
title: "report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set Up

```{r libraries}
library(here)
library(tidyverse)
library(ggplot2)
library(cowplot)
library(fitdistrplus)
library(dplyr)
library(broom)
library(MASS)
library(sjPlot)
library(sjmisc)
library(jtools)
library(interactions)
library(scico)
library(ordinal)
library(gghalves)
library(patchwork)
library(sure)
library(countreg)
library(ggeffects)
library(effects)
```

## Importing and Wrangling of Data

Publicly available sample child interview datasets from years 2020 and 2019 were extracted from the Centers for Disease Control and Prevention website. The interviews are conducted on a yearly basis as a part of the National Health Interview Survey carried out by National Center for Health Statistics throughout the US. After filtering entries with missing values, the final sample size was 4,485 adolescents between age 10 and 17. The average age was 13.62 ⩲ 2.28 years SD.


```{r data, message=FALSE}
child_2020 <- read_csv("child20.csv")
child_2019 <- read_csv("child19.csv")
```

Selecting the target columns and renaming them 
```{r adjusting the dataset, message=FALSE}
child_data <- full_join(child_2019, child_2020) %>% #joining data from 2019 and 2020
  rename(age=AGEP_C, 
         SDQ_peer = SDQPEER_C, SDQ_total = SDQTOT_C, 
         violence=VIOLENEV_C, parent_jailed = JAILEV_C, MHI_home= MENTDEPEV_C, addict_home=ALCDRUGEV_C, 
         food_security=FDSCAT4_C, poverty_ratio=RATCAT_C) %>%
  dplyr::select(age, SDQ_peer, SDQ_total, violence, parent_jailed, MHI_home, addict_home, food_security, poverty_ratio)

```


Filtering the dataset based on age (only 10yo and older) and calculating some new variables based on given information 

```{r}
#getting rid of entries with NA values in crucial cols & selecting only above 9 yo
adolescents <- child_data %>%
  filter(!is.na(SDQ_peer)) %>% #includes data about friendships
  filter(age > 9) %>% #selecting only adolescents (i.e. 10 and above)
  filter(SDQ_total < 40) %>% #max value of SDQ = 40
  filter(SDQ_peer!=88) %>%
  filter(food_security!=8) %>%
  mutate(SDQ_30 = SDQ_total - SDQ_peer, 
         poverty_recoded = ifelse(poverty_ratio<6, (4-((poverty_ratio-1)*0.8)), 0), 
         food_sec_recoded = (food_security-1)*1.33,
         violence = ifelse(violence==2, 0, 1), parent_jailed = ifelse(parent_jailed==2, 0, 1), MHI_home = ifelse(MHI_home==2, 0, 1), addict_home = ifelse(addict_home==2, 0, 1),
         early_life_stress = (violence + parent_jailed + MHI_home + addict_home), 
         cumulative_trauma = (poverty_recoded + food_sec_recoded + early_life_stress),
         peer_problems = ifelse(SDQ_peer==0, "none", ifelse(SDQ_peer < 4, "mild", ifelse(SDQ_peer < 7, "moderate", "severe")))) %>%
  relocate(age, SDQ_total, SDQ_30, SDQ_peer, peer_problems)


sample_size <- nrow(adolescents)

print(sample_size)
```

# Basic Data Summaries and Explorations

```{r}
summaries <- adolescents %>% 
  group_by(SDQ_peer) %>% 
  summarise(n = n(), mean_30 = round(mean(as.numeric(SDQ_30)),3), sd_30 = round(sd(as.numeric(SDQ_30)),3), median_30=median(as.numeric(SDQ_30)), 
            mean_ct = round(mean(cumulative_trauma), 3), sd_ct = round(sd(cumulative_trauma),3), median_ct = round(median(cumulative_trauma), 3))

summaries_overall <- adolescents %>% 
  summarise(mean_30 = round(mean(as.numeric(SDQ_30)),3), sd_30 = round(sd(as.numeric(SDQ_30)),3), median_30=median(as.numeric(SDQ_30)), 
            mean_ct = round(mean(cumulative_trauma), 3), sd_ct = round(sd(cumulative_trauma),3), median_ct = round(median(cumulative_trauma), 3),
            mean_PP = round(mean(as.numeric(SDQ_peer)),3), sd_PP = round(sd(as.numeric(SDQ_peer)),3), median_pp = round(median(SDQ_peer), 3))

write_csv(summaries, "summary_table.csv")
```

## Age Distribution
```{r}
age_graph <- ggplot(adolescents, aes(x=age)) +
  geom_bar(fill="darksalmon") +
  theme_cowplot() +
  background_grid(major="y", minor="y") +
  scale_x_continuous(breaks = c(10,11,12,13,14,15,16,17)) +
  theme(legend.position = "none", plot.title = element_text(size=12), axis.title = element_text(size=10)) +
  labs(x="Age", y="Count", title="Distribution of age") 
  
  
ggsave("age.png", plot=age_graph, units = "cm", width = 11, height = 8.5, dpi = "retina", 
       device = "png", path = here())

age_graph

mean(adolescents$age)
sd(adolescents$age)
```


## Exploring used variables and their distribution
### SDQ 30 - depedent variable
```{r}
response_graph <- ggplot(adolescents, aes(x=SDQ_30)) +
  geom_bar(fill="thistle") +
  theme_cowplot() +
  background_grid(major="y", minor="y") +
  theme(legend.position = "none", plot.title = element_text(size=12), axis.title = element_text(size=10)) +
  labs(x="SDQ 30 score", y="Count", title="Distribution of response variable (SDQ 30 score)") 

SDQ_high_graph <- ggplot(subset(adolescents, SDQ_30 > 19), aes(x=SDQ_30)) +
  geom_bar(fill="thistle") +
  geom_text(data=subset(adolescents, SDQ_30 > 22), stat='count', aes(label=..count..), vjust=-0.5, color="grey") +
  theme_cowplot() +
  background_grid(major="y", minor="y") +
  theme(legend.position = "none", 
        axis.title = element_blank(), axis.text = element_text(size=9), 
        plot.background = element_rect(fill="white", size=0.8, color="gray", linetype=3)) +
  scale_x_continuous(breaks = c(20, 22, 24, 26, 28, 30))  +
  scale_y_continuous(breaks=c(0, 5, 10, 15)) 

response_graph <- response_graph + inset_element(SDQ_high_graph, left = 0.5, bottom = 0.4, right = 1, top = 1)


ggsave("response_graph .png", plot=response_graph, units = "cm", width = 14, height = 10, dpi = "retina", 
       device = "png", path = here())

response_graph
```

#### Fitting PDF
```{r}
fit_geom <- fitdist(adolescents$SDQ_30, "geom")
plot(fit_geom)
```


### Cumulative trauma - independent variable
```{r version 1}
trauma_graph <- ggplot(adolescents, aes(x=cumulative_trauma)) +
  geom_bar(fill="#CC6666", width=0.1) +
  theme_cowplot() +
  background_grid(major="y", minor="y") +
  theme(legend.position = "none", plot.title = element_text(size=12, face="bold"), axis.title = element_text(size=10)) +
  labs(x="Cumulative trauma", y="Count", title="Distribution of cumulative trauma across the sample") +
  scale_x_continuous(breaks = c(0,1,2,3,4,5,6,7,8,9,10,11))
  

high_trauma_graph<- ggplot(subset(adolescents, cumulative_trauma >= 5), aes(x=cumulative_trauma)) +
  geom_bar(fill="#CC6666", width=0.09) +
  theme_cowplot() +
  background_grid(major="y", minor="y") +
  theme(legend.position = "none", 
        axis.title = element_blank(), axis.text = element_text(size=9), 
        plot.background = element_rect(fill="white", size=0.8, color="gray", linetype=3)) +
  scale_x_continuous(breaks = c(5, 6,7,8,9,10,11))

trauma_graph <- trauma_graph + inset_element(high_trauma_graph, left = 0.5, bottom = 0.4, right = 1, top = 1)

ggsave("trauma_graph.png", plot=trauma_graph, units = "cm", width = 14, height = 10, dpi = "retina", 
       device = "png", path = here())

trauma_graph
```

```{r version 2}
trauma_graph_violin <- ggplot(adolescents %>% mutate(dummy=1), aes(x=dummy, y=cumulative_trauma)) + 
  # violin plot
  geom_half_violin(aes(x=dummy+0.06), fill="#CC6666", alpha =0.9, color=NA, side = "r") +
  # single subject data points (1 per participant) with horizontal jitter
  geom_point(aes(x=dummy-0.1), position = position_jitter(width =0.04, height = 0.1), shape=16, size = 1) +
  # boxplot of distribution (median, 1st and 3rd quartile)
  geom_boxplot(width = .08, outlier.shape = NA) +
  # adding plot of mean and SEM  
  stat_summary(fun = mean, geom = "point", size=1, shape = 16,
               position = position_nudge(+.06), colour = "black") + 
  stat_summary(fun.data = mean_se, geom = "errorbar",
               position = position_nudge(+.06), colour = "black", width = 1, size = 1) +
  # correcting labels
  labs(x = '', y = 'Cumulative Trauma (0-12)', title = 'Distribution of cumulative trauma scores') +
  # aesthetical changes
  theme_cowplot() +
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(),
        axis.title.x = element_text(size=11),
        axis.text.x = element_text(size=10),
        aspect.ratio = 1, 
        plot.title = element_text(face="bold", size=12)) +  
  scale_y_continuous(breaks = c(0,1,2,3,4,5,6,7,8,9,10,11, 12), limits = c(-0.2,12)) +
  scale_x_continuous(limits = c(0.85, 1.45)) +
  coord_flip() 

ggsave("trauma_graph_violin.png", plot=trauma_graph_violin, units = "cm", width = 10, height = 10, dpi = "retina", 
       device = "png", path = here())

trauma_graph_violin
```


### Peer problems score
```{r}
peers_graph_overall <- ggplot(adolescents, aes(x=SDQ_peer, fill=peer_problems)) +
  geom_bar(width=0.9, fill=c("#875F79")) +
  theme_cowplot() +
  background_grid(major="y", minor="y") +
  theme(legend.position = "none", plot.title = element_text(size=12, vjust=6), axis.title = element_text(size=10)) +
  labs(x="Problems with peer relationships", y="Count", title="Distribution of SDQ Peer Problems Subscale Scores") +
  scale_x_continuous(breaks = c(0,1,2,3,4,5,6,7,8,9,10)) 

peers_graph_high <- ggplot(subset(adolescents, SDQ_peer > 4), aes(x=SDQ_peer)) +
  geom_bar(fill="#875F79", width=0.9) +
  geom_text(stat='count', aes(label=..count..), vjust=-0.8, color="grey") +
  theme_cowplot() +
  background_grid(major="y", minor="y") +
  theme(legend.position = "none", plot.title = element_text(size=12), axis.title = element_text(size=10), axis.text = element_text(size=9), plot.background = element_rect(fill="white", size=0.8, color="gray", linetype=3)) +
  labs(x=" ", y=" ") +
  scale_x_continuous(breaks = c(5,6,7,8,9,10))  +
  scale_y_continuous(breaks=c(0, 20, 40, 60, 80))

peers_graph <- peers_graph_overall + inset_element(peers_graph_high, left = 0.5, bottom = 0.4, right = 1, top = 1.05)

ggsave("peer_graph.png", plot=peers_graph, units = "cm", width = 14, height = 10, dpi = "retina", 
       device = "png", path = here())

peers_graph
```


#### check for collinearity
```{r}
ggplot(adolescents, aes(x=as.numeric(SDQ_peer), y=cumulative_trauma)) +
  geom_jitter(width=0.4) +
  geom_smooth(stat = "smooth", method="glm")
```



## First plotting of the data
```{r}
distribution <- ggplot(adolescents, aes(x=cumulative_trauma, y=as.numeric(SDQ_30), color=as.factor(SDQ_peer))) +
  geom_jitter(width=0.3) +
  scale_color_scico_d(palette = 'batlow', begin=0, end=1) +
  theme_classic() +
  background_grid(minor = "xy") +
  labs(x="Cumulative trauma", y="SDQ 30 score", title="Data", color="Peer problems") +
  theme(plot.title = element_text(size=12, face="bold"), legend.position = "none") +
  #guides(col = guide_legend(nrow = 1)) +
  scale_y_continuous(breaks=c(0, 5, 10, 15, 20, 25, 30)) +
  scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12)) 

ggsave("data_graph.png", plot=distribution, units = "cm", width = 15, height = 10.5, dpi = "retina", 
       device = "png", path = here())

distribution
```

```{r}
distribution_facet <- ggplot(adolescents, aes(x=cumulative_trauma, y=as.numeric(SDQ_30), color=as.factor(SDQ_peer))) +
  geom_jitter(width=0.3, size=0.65) +
  scale_color_scico_d(palette = 'batlow', begin=0, end=1) +
  theme_classic() +
  background_grid(minor = "xy", size.major=0.2, size.minor=0.1) +
  labs(x="Cumulative trauma", y="SDQ 30 score", title="", color="Peer problems") +
  theme(plot.title = element_text(size=12, face="bold"), legend.position = "none") +
  #guides(col = guide_legend(nrow = 1)) +
  scale_y_continuous(breaks=c(0, 5, 10, 15, 20, 25, 30)) +
  scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12)) +
  facet_wrap(~SDQ_peer, nrow = 2) +
  geom_smooth(method=glm, se=FALSE, color="red", size=0.5)

ggsave("data_graph_facet.png", plot=distribution_facet, units = "cm", width = 17, height = 7.5, dpi = "retina", 
       device = "png", path = here())

distribution_facet
```




# Analysis

## Poisson regression 

```{r}
adolescents$SDQ_peer <- as.factor(adolescents$SDQ_peer)

interaction_model_poisson <- glm(SDQ_30 ~ cumulative_trauma*SDQ_peer, data=adolescents, family=poisson(link="log"))

poisson_summary <- summary.glm(interaction_model_poisson)
summ(interaction_model_poisson)

#checking on overdispersion
dispersion_poisson <- poisson_summary$deviance / poisson_summary$df.residual
if (dispersion_poisson > 2){
  print("Overdispersion!")
} else {
  print("You good on dispersion.")
}

```

## Negative Binomial Model
```{r}
fit_nbinom <- fitdist(adolescents$SDQ_30, "nbinom")
plot(fit_nbinom)

interaction_model_negbi <- glm.nb(formula = SDQ_30 ~ cumulative_trauma * SDQ_peer, data = adolescents)

nb_summary <- summary(interaction_model_negbi)
nb_summary 

#checking for overdispersion
dispersion_nb <- nb_summary$deviance / nb_summary$df.residual

if (dispersion_nb > 2){
  print("overdispersion!")
} else {
  print("You good on dispersion.")
}
```


```{r}
#checking model fit
hist(rstandard(interaction_model_negbi), main = "Distribution of residuals", xlab="Residuals")
plot(interaction_model_negbi,2)
plot(rstandard(interaction_model_negbi),type="l")
rootogram(interaction_model_negbi, max=30)
```


```{r checking with reduced model}
#checking against reduced model
control_model_negbi <- glm.nb(SDQ_30 ~ cumulative_trauma+SDQ_peer, data=adolescents)


#checking difference between the two models
LL_interaction <- logLik(interaction_model_negbi)
LL_control <- logLik(control_model_negbi)
delta_2 <- 2*(LL_interaction-LL_control)
1-pchisq(delta_2, 10)

#double check 
anova(interaction_model_negbi, control_model_negbi, test="LRT")
```


```{r checking with each predictor}
#checking with each predictor

#cumulative trauma only
CT_model_negbi <- glm.nb(SDQ_30 ~ cumulative_trauma, data=adolescents)

#checking difference between the two models
LL_var <- logLik(CT_model_negbi)
LL_control <- logLik(control_model_negbi)
delta_2 <- 2*(LL_control-LL_var)
1-pchisq(delta_2, 10)

#double check 
anova(control_model_negbi, CT_model_negbi, test="LRT")


#peer problems only
PP_model_negbi <- glm.nb(SDQ_30 ~ SDQ_peer, data=adolescents)

#checking difference between the two models
LL_var <- logLik(PP_model_negbi)
LL_control <- logLik(control_model_negbi)
delta_2 <- 2*(LL_control-LL_var)
1-pchisq(delta_2, 1)

#double check 
anova(control_model_negbi, PP_model_negbi, test="LRT")
```

### New reduced NB model 
```{r}
hist(rstandard(control_model_negbi), main = "Distribution of residuals", xlab="Residuals")
plot(control_model_negbi,2)
plot(rstandard(control_model_negbi),type="l")
rootogram(control_model_negbi, max=30, main = "Negative Binomial Model: Observed vs Fitted Values", xlab="SDQ 30")
```

```{r}

#playing with different summaries
summary_negbi <- summary(control_model_negbi)
summary_negbi 
anova(control_model_negbi)
summ(control_model_negbi)

export_summs(control_model_negbi)
summary(allEffects(control_model_negbi))

```


### Plotting of the model predictions
```{r}
model_predict <- data.frame(ggpredict(control_model_negbi,  terms = c("cumulative_trauma", "SDQ_peer")))

model_graph <- ggplot(model_predict, aes(x = x, y = predicted, colour = group, fill = group)) +
  # plotting the prediction
  geom_line(size = 0.75) +
  # plotting the confidence levels
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, xmin=0, xmax=12), alpha = .1, linetype=0) +
  # setting up color and fill palette - scico tokyo 
  scale_color_scico_d(palette = 'batlow', begin=0, end=1) +
  scale_fill_scico_d(palette = 'batlow', begin=0, end=1) +
  # changing limits, breaks and labels of both axis 
  scale_x_continuous(breaks = c(0,2,4,6,8,10,12), limits = c(0, 12)) +
  scale_y_continuous(breaks = c(0,10,20,30, 40, 50, 60, 70)) +
  # background setting
  theme_classic() +
  # changing labels and title
  labs(x="Cumulative trauma", title="Negative Binomial Model Predictions", 
      color="Peer \nproblems", fill="Peer \nproblems") +
  theme(axis.text = element_text(size=11), axis.title = element_text(size=12), 
        axis.title.y = element_blank(),
        legend.title = element_text( size=10), legend.text=element_text(size=10), legend.key.size = unit(0.5, 'cm'),
        plot.title = element_text(size=12, face="bold")) +
  geom_hline(yintercept=30, size=0.5, linetype=2, alpha=0.5)

model_graph

ggsave("model_graph.png", plot=model_graph, units = "cm", width = 15, height = 11, dpi = "retina", 
       device = "png", path = here())
```

```{r}
data_prediction <- distribution + model_graph &
  theme(plot.tag = element_text(size = 8), plot.title = element_text(size=12, face="italic")) &
  plot_annotation(tag_levels = 'A', 
                  title="The effects of cumulative trauma and peer problems on SDQ 30 score",
                  theme = theme(plot.title = element_text(size = 12, face="bold")))

ggsave("data_prediction.png", plot=data_prediction, units = "cm", width = 15, height = 8.5, dpi = "retina", 
       device = "png", path = here())

data_prediction
```


## Hurdle

```{r}
interaction_model_hurdle <- hurdle(formula = SDQ_30 ~ cumulative_trauma * SDQ_peer, data = adolescents, dist ="geometric")

hurdle_summary <- summary(interaction_model_hurdle)
hurdle_summary 

qqrplot(interaction_model_hurdle)
rootogram(interaction_model_hurdle, max = 30)
hist(interaction_model_hurdle$residuals)

control_model_hurdle <- hurdle(formula = SDQ_30 ~ cumulative_trauma + SDQ_peer, data = adolescents, dist ="geometric")

LL_int <- logLik(interaction_model_hurdle)
LL_control <- logLik(control_model_hurdle)
delta_2 <- 2*(LL_int-LL_control)
1-pchisq(delta_2, 1)

AIC(control_model_negbi, control_model_hurdle)
```

Hurdle model looks like a pretty good fit but residuals not really symmetrically distributed - still rightward skewed 
When tested against final NegBi model, it has higher AIC 

## CLM

```{r}
adolescents$SDQ_30 <- as.ordered(adolescents$SDQ_30)

clm_model <- clm(SDQ_30 ~ cumulative_trauma*SDQ_peer, data=adolescents)
summary(clm_model)
anova(clm_model)

scale_test(clm_model)
```

```{r}
clm_model_control <- clm(SDQ_30 ~ cumulative_trauma+SDQ_peer, data=adolescents)

LL_interaction <- logLik(clm_model)
LL_control <- logLik(clm_model_control)
delta_2 <- 2*(LL_interaction-LL_control)
1-pchisq(delta_2, 10)

anova(clm_model_control, clm_model, test="Chisq")
```

### Plotting of the final model
```{r}
new_data <- data.frame("cumulative_trauma"=c(0:12), "SDQ_peer"=as.factor(0))
predicted <- data.frame(predict(clm_model,new_data,type = "p")) %>% mutate(cumulative_trauma=c(0:12), SDQ_peer=as.factor(0)) 

for (i in 1:10) {
  new_data <- data.frame("cumulative_trauma"=c(0:12), "SDQ_peer"=as.factor(i))
  predicted_new <- data.frame(predict(clm_model,new_data,type = "p")) %>% mutate(cumulative_trauma=c(0:12), SDQ_peer=as.factor(i)) 
  predicted <- full_join(predicted, predicted_new)
}

predicted <- predicted %>% 
  relocate(cumulative_trauma, SDQ_peer) %>%
  rename_with(~ gsub("fit.", "SDQ_", .x, fixed = TRUE)) %>%
  pivot_longer(cols = SDQ_0:SDQ_29, names_to = "SDQ_30", values_to = "probability") %>%
  mutate(probability = probability*100)

predicted$SDQ_30 <- factor(predicted$SDQ_30,
                           levels = c("SDQ_0", "SDQ_1", "SDQ_2", "SDQ_3", "SDQ_4", "SDQ_5", "SDQ_6", "SDQ_7", "SDQ_8", "SDQ_9", 
                                      "SDQ_10", "SDQ_11", "SDQ_12", "SDQ_13", "SDQ_14", "SDQ_15", "SDQ_16", "SDQ_17", "SDQ_18", "SDQ_19",
                                      "SDQ_20", "SDQ_21", "SDQ_22", "SDQ_23", "SDQ_24", "SDQ_25", "SDQ_26", "SDQ_27", "SDQ_28", "SDQ_29"))
  
  
probabilities <- ggplot(predicted, aes(x=cumulative_trauma, y=probability, fill=SDQ_peer)) +
  geom_area() +
  theme_classic() +
  scale_x_continuous(breaks = c(0,4,8,12)) +
  scale_fill_scico_d(palette = 'batlow', begin=0, end=1) +
  facet_wrap(.~ordered(SDQ_30), ncol = 7) +
  labs(x = "Cumulative trauma", y="Probability", fill="Peer \nproblems") +
  theme(legend.title = element_text(size=10), legend.text=element_text(size=8), legend.key.size = unit(0.4, 'cm'))
  

ggsave("probabilities.png", plot=probabilities, units = "cm", width = 25, height = 15.5, dpi = "retina", 
       device = "png", path = here())  


ggplot(predicted, aes(x=cumulative_trauma, y=probability, color=SDQ_peer, fill=SDQ_peer)) +
  geom_line() +
  theme_classic() +
  scale_x_continuous(breaks = c(0,4,8,12)) +
  scale_color_scico_d(palette = 'batlow', begin=0, end=1) +
  scale_fill_scico_d(palette = 'batlow', begin=0, end=1) +
  facet_wrap(.~ordered(SDQ_30)) +
  labs(x = "Cumulative trauma", y="Probability")
```


```{r}
#model fit
hist(resids(clm_model), main = "Distribution of residuals", xlab="Residuals")
autoplot.clm(clm_model, what = "qq") + 
  theme_bw() + 
  labs(title = "Normal Q-Q") + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
plot(resids(clm_model),type="l")
```


```{r, eval=FALSE}
#alternative plotting 
plot_model(clm_model, type="int", colors = scico(11, palette = "batlow")) +
  scale_x_continuous(breaks=c(0,4,8,12)) +
  theme(axis.text = element_text(size = 8), axis.title.y = element_blank()) +
  labs(legend = "Peer \nproblems", x="Cumulative Trauma (0-12)", title = "Predicted probabilities of SDQ 30")


plot_model(clm_model, terms="cumulative_trauma", type="eff") +
  scale_x_continuous(breaks = c(0,2,4,6,8,10,12)) +
  labs(x="Cumulative Trauma (0-12)") + 
  theme(axis.title.y = element_blank())

```

